---
title: "Summary of Dating App Experiences in 2022"
author: "Isaac Baca"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction: 

This is a two part project summarizing my experience using three different dating apps in the year 2022.  

1. In part one of this project, I use SQL queries to select, count, filter, group, aggregate, and summarize the data.

2. [In part two of this project](https://public.tableau.com/app/profile/isaac5041/viz/SummaryofDatingAppExperiencesin2022/Dashboard2), I use Tableau to create a dashboard visualizing the data obtained from the SQL queries.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(odbc)
library(DBI)
library(tidyverse)
library(RSQLite)
```


```{r include=FALSE}
Dating = read_excel("/Volumes/Vandy Main/Data/Dating Apps/2022/app_data.xlsx")
```


```{r include=FALSE}
Dating$enjoyment = as.numeric(Dating$enjoyment)
Dating$paid = as.numeric(Dating$paid)
Dating$cost = as.numeric(Dating$cost)
Dating$amount_me = as.numeric(Dating$amount_me)
Dating$amount_her = as.numeric(Dating$amount_her)
```


```{r include=FALSE}
con <- dbConnect(drv = RSQLite::SQLite(),
                 dbname = ":memory:")

#store sample data in database
dbWriteTable(conn = con, 
             name = "apps",
             value = Dating)


#remove the local data from the environment
rm(Book3)
```


---

<a name="one"><a/>

## View the table

---

#### View the `apps` table.

```{sql echo=TRUE, connection=con, output.var="apps"}
SELECT *
FROM apps
LIMIT 5;
```
```{R, echo=FALSE}
print(apps)
```


---

#### Count the total number of matches.

```{sql echo=TRUE, connection=con, output.var="matches"}
SELECT COUNT(Name) AS count_matches
FROM apps;
```
```{R, echo=FALSE}
print(matches)
```


---

#### Count the total number of matches grouped by app.

```{sql echo=TRUE, connection=con, output.var="matches_by_app"}
SELECT app AS App, COUNT(Name) AS count_of_matches
FROM apps
GROUP BY app
ORDER BY app
```
```{R, echo=FALSE}
print(matches_by_app)
```


---

#### Count the total number of conversations.

```{sql echo=TRUE, connection=con, output.var="convos"}
SELECT COUNT(first_response) AS count_of_convos
FROM apps
WHERE first_response = 'yes';
```
```{R, echo=FALSE}
print(convos)
```


---

#### Count the total number of conversations grouped by app.

```{sql echo=TRUE, connection=con, output.var="convos_by_app"}
SELECT app AS App, COUNT(first_response) AS count_of_convos
FROM apps
WHERE first_response = 'yes'
GROUP BY app
ORDER BY app
```
```{R, echo=FALSE}
print(convos_by_app)
```


---

#### Count the total number of numbers exchanged.

```{sql echo=TRUE, connection=con, output.var="number"}
SELECT COUNT(phone_number) AS count_number_exchanged
FROM apps
WHERE phone_number = 'yes';
```
```{R, echo=FALSE}
print(number)
```


---

#### Count the total number of numbers exchanged by app.

```{sql echo=TRUE, connection=con, output.var="number_by_app"}
SELECT app AS App, COUNT(phone_number) AS count_number_exchanged
FROM apps
WHERE phone_number = 'yes'
GROUP BY app
ORDER BY app
```
```{R, echo=FALSE}
print(number_by_app)
```


---

#### Count the total number of first dates.

```{sql echo=TRUE, connection=con, output.var="dates"}
SELECT COUNT(first_date) AS count_first_date
FROM apps
WHERE first_date = 'yes';
```
```{R, echo=FALSE}
print(dates)
```


---

#### Count the total number of first dates by app.

```{sql echo=TRUE, connection=con, output.var="first_by_app"}
SELECT app AS App, COUNT(first_date) AS count_first_dates
FROM apps
WHERE first_date = 'yes'
GROUP BY app
ORDER BY app
```
```{R, echo=FALSE}
print(first_by_app)
```


---

#### Count the total number of second dates.

```{sql echo=TRUE, connection=con, output.var="dates2"}
SELECT COUNT(second_date) AS count_second_date
FROM apps
WHERE second_date = 'yes';
```
```{R, echo=FALSE}
print(dates2)
```


---

#### Count the total number of second dates by app.

```{sql echo=TRUE, connection=con, output.var="second_by_app"}
SELECT app AS App, COUNT(second_date) AS count_second_dates
FROM apps
WHERE second_date = 'yes'
GROUP BY app
ORDER BY app
```
```{R, echo=FALSE}
print(second_by_app)
```


---

#### Calculate the total/average amount of money spent.

```{sql echo=TRUE, connection=con, output.var="money_spent"}
SELECT SUM(amount_me) AS total_money_spent_by_me, SUM(amount_me)/COUNT(first_date) AS avg_spent_per_date
FROM apps
WHERE first_date = 'yes';
```
```{R, echo=FALSE}
print(money_spent)
```


---

#### View a table with the total money spent and the amount spent by each person.

```{sql echo=TRUE, connection=con, output.var="cost2"}
SELECT app AS App, cost AS total_cost_of_date, amount_me AS amount_I_paid, amount_her AS amount_she_paid
FROM apps
WHERE first_date = 'yes'
ORDER BY cost DESC
```
```{R, echo=FALSE}
print(cost2)
```


---

#### View a table of my enjoyment of the dates grouped by app (from 1-10)

```{sql echo=TRUE, connection=con, output.var="enjoyment"}
SELECT app AS App, enjoyment AS My_enjoyment
FROM apps
WHERE first_date = 'yes'
ORDER BY enjoyment DESC;
```
```{R, echo=FALSE}
print(enjoyment)
```


---


This concludes part one of this project.  [Click here](https://public.tableau.com/app/profile/isaac5041/viz/SummaryofDatingAppExperiencesin2022/Dashboard2) to view part two:  the data visualization in Tableau.

---
